Variation in site entropy explains differences in structure-sequence relationships of proteins

### 2015-05-31 manuscript/manuscript.tex
Adding figures

\begin{abstract}
{\color{red}Recent work has shown that structural properties are capable of predicting site-specific sequence variability for a given protein. However, the strength and significance of these structure-sequence relations appear to vary widely among different proteins, with absolute correlation strengths ranging from $0.1$ to $0.8$. }
\end{abstract}
\vfill
\vfill
\def\thefootnote{\fnsymbol{footnote}}
\setcounter{footnote}{0}

@@

Figures that are still needed...
Table 1 - First make a new table with the mean values Entropy
Table 2 - First make a new table with the mean values Rate4Site

@@

\begin{center}
	\begin{table}[H]
	\begin{tabular}{| p{1.5cm} | p{2.5cm} | p{2cm} | p{2cm} |  }
		\hline
		Dataset & Mean $\rho$ Rate4Site-CN  & Mean $\rho$ Rate4Site-WCN & Mean $\rho$ Rate4Site-RSA \\
		\hline	
		Enzyme &  $-0.445$  & $-0.432$ & $0.464$ \\
		\hline
		Virus & $-0.213$ & $-0.217$ & $0.237$ \\
		\hline	
	\end{tabular}
	\caption{NEED A CAPTION}0.07859
	\label{table:entropy_stats}
	\end{table}
\end{center}

%Should I report the intercept%
\begin{center}
	\begin{table}[H]
	\begin{tabular}{ | p{5.0cm} | p{3cm} | p{3cm} | p{3cm} | }
	\hline
	Model & Coefficient x  & Coefficient y & Coefficient z \\	
	\hline
	CN-Entropy $\rho$ $ = $ Mean Entropy + Dataset + Dataset*Mean Entropy & $0.079 ^{**}$ & $0.382^{***}$  & $-0.583$ \\	
	\hline
	WCN-Entropy $\rho$ $ = $ Mean Entropy + Dataset + Dataset*Mean Entropy & $0.049$ & $0.323^{***}$ & $-0.568$  \\	
	\hline
	RSA-Entropy $\rho$ $ = $ Mean Entropy + Dataset + Dataset*Mean Entropy &  $-0.0300$ & $-0.336^{***}$ & $0.903^{*}$ \\

@@

Need a two panel figure \\
First plot the mean entropy vs the variance of entropy (then pick points that are in each of the four corners). This is B. I need to circle these by pointing an additional geom point and open circles and put numbers.  \\
Pick these proteins and then plot the distributions. This is A. \\
Basically this figure will highlight the difference between mean entropy and variance in entropy. \\

In the introduction and abstract need to better highlight the two papers (Yeh and Shah) that contradict on the surface and they do not. Hold off on Rate4Site for Now.

>>>>

\begin{abstract}
{\color{red}Recent work has shown that structural properties are capable of predicting site-specific sequence variability for a given protein. However, the strength and significance of these structure-sequence relations appear to vary widely among different proteins, with absolute correlation strengths ranging from $0.1$ to $0.8$.  In the introduction and abstract need to better highlight the two papers (Yeh and Shah) that contradict on the surface and they do not. Hold off on Rate4Site for Now.}
\end{abstract}
\vfill
\vfill
\def\thefootnote{\fnsymbol{footnote}}
\setcounter{footnote}{0}

@@

        \begin{figure}[H]
            \centerline{\includegraphics[width=7.5in]{protein_ex_plot.pdf}}     
            \caption{NEED A CAPTION!!!. Basically this figure will highlight the difference between mean entropy and variance in entropy.}
            \label{fig:protein_ex_plot}
    \end{figure}

@@

\begin{center}
	\begin{table}[H]
	\begin{tabular}{| p{1.5cm} | p{2.5cm} | p{2cm} | p{2cm} |  }
		\hline
		Dataset & Mean $\rho$ Rate4Site-CN  & Mean $\rho$ Rate4Site-WCN & Mean $\rho$ Rate4Site-RSA \\
		\hline	
		Enzyme &  $-0.445$  & $-0.432$ & $0.464$ \\
		\hline
		Virus & $-0.213$ & $-0.217$ & $0.237$ \\
		\hline	
	\end{tabular}
	\caption{NEED A CAPTION}
	\label{table:entropy_stats}
	\end{table}
\end{center}

%Should I report the intercept%
\begin{center}
	\begin{table}[H]
	\begin{tabular}{ | p{5.0cm} | p{3cm} | p{3cm} | p{3cm} | }
	\hline
	Model & Coefficient x  & Coefficient y & Coefficient z \\	
	\hline
	CN-Entropy $\rho$ $ = $ Mean Entropy + Dataset + Dataset*Mean Entropy & $0.079 ^{**}$ & $0.382^{***}$  & $-0.583$ \\	
	\hline
	WCN-Entropy $\rho$ $ = $ Mean Entropy + Dataset + Dataset*Mean Entropy & $0.049$ & $0.323^{***}$ & $-0.568$  \\	
	\hline

	RSA-Entropy $\rho$ $ = $ Mean Entropy + Dataset + Dataset*Mean Entropy &  $-0.0300$ & $-0.336^{***}$ & $0.903^{*}$ \\

@@
